LogChunks: A Data Set for Build Log Analysis

### 2020-03-12 msr-paper/paper.tex

\section{Introduction}
Continuous Integration (CI) has become a common practice in software
engineering~\cite{hilton2016usage}.  Many software projects use
CI~\cite{hilton2016usage,staahl2014modeling,beller2017oops} to detect
bugs early~\cite{vasilescu2015quality,duvall2007continuous}, improve
developer productivity~\cite{miller2008hundred,hilton2016usage} and
communication~\cite{downs2012ambient}.  CI builds produce logs which
report results of various sub-steps within the build.  These build logs
contain a lot of valuable information for developers and researchers---for example, descriptions of compile errors, linter warnings or failed
tests~\cite{beller2017oops,seo2014programmers,vassallo2017a-tale}.

@@

For \logchunks, we queried GHTorrent from 2018-04-01 for the three
most popular repositories of each of the 30 most popular languages
to cover a broad range of development languages.
Among the resulting repositories are, for example, \texttt{git/git},
\texttt{Microsoft/TypeScript} and \texttt{jwilm/alacritty}.

>>>>

\section{Introduction}
Continuous Integration (CI) has become a common practice in software
engineering~\cite{hilton2016usage}.  Many software projects use
CI~\cite{hilton2016usage,staahl2014modeling,beller2017oops} to detect
bugs early~\cite{vasilescu2015quality,duvall2007continuous}, improve
developer productivity~\cite{miller2008hundred,hilton2016usage} and
communication~\cite{downs2012ambient}.  CI builds produce logs which
report results of various sub-steps within the build.  These build logs
contain a lot of valuable information for developers and researchers---for example, descriptions of compile errors or failed
tests~\cite{beller2017oops,seo2014programmers,vassallo2017a-tale}.

@@

For \logchunks, we queried GHTorrent from 2018-04-01 for the three
most popular repositories of each of the 30 most popular languages
to cover a broad range of development languages.
Among the resulting repositories are, for example,
\texttt{Microsoft/TypeScript}, \texttt{git/git} and \texttt{jwilm/alacritty}.
